taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-03-06 paper/manuscript.Rmd
WIP

@@

```{r}
bbs_ids %>% filter(is.na(ott) & !is.na(ids_post_clean))
```

@@

>>>>

Synonyms vs accepted names. How many species of chameleons are described?

Inconsistencies: errors or disputes? Taxon concepts.

-----

@@

```{r}
bbs_cleaned_ids %>% filter(is.na(ott) & !is.na(ids_post_clean))
```

@@

Alternately, sticking with the standard `dwc` schema:

```{r}
iucn_ids <- unmatched$species %>% ids("iucn") %>% select(acceptedNameUsageID) %>% distinct()
right_join(taxa_tbl("iucn"), iucn_ids, copy=TRUE, by ="acceptedNameUsageID") %>% 
  select(scientificName, taxonomicStatus, acceptedNameUsageID, taxonRank, taxonID)
```
